DOpElib:\\ Differential Equations and Optimization Environment

### 2013-12-13 Examples/PDE/StatPDE/Example7/content.tex
Ueberarbeitung PDE Statpde examples mit Ausnahme von 9 und 10.

From the previous examples we know how to read a grid from an \textit{.inp} file. The grid of our current example comes from the above mentioned benchmark problem. The parameter file (\textit{dope.prm}) contains the same variables as in the first two examples.\\
Apart from different point values of derivatives of the solution, we want to evaluate an integral over part of the boundary. \index{functional} \index{functional!boundary integral} This is newly implemented in \textit{functionals.h}.\\
The (linear) elasticity equation is much simpler than the FSI problems we treated before, which can be seen in \textit{localpde.h} where the \texttt{ElementEquation} and \texttt{ElementMatrix} are implemented. In principle, everything is clear from the preceding examples.\\
The \textit{main.cc} file does not contain any innovation, either. Here, we refine the grid globally instead of using an error estimator for local refinement.\\
The output of the program reflects again the linearity of the problem (only one Newton step is needed for solution).\\

>>>>

From the previous examples we know how to read a grid from an \textit{.inp} file. The grid of our current example comes from the above mentioned benchmark problem.\\
Apart from different point values of derivatives of the solution, we want to evaluate an integral over part of the boundary. \index{functional} \index{functional!boundary integral}This is newly implemented in \textit{functionals.h}.\\
In principle, everything is clear from the preceding examples. We refine the grid globally instead of using an error estimator for local refinement.
The output of the program reflects again the linearity of the problem (only one Newton step is needed for solution).\\

### 2013-12-13 Examples/PDE/StatPDE/Example9/content.tex
Ueberarbeitung PDE Statpde examples mit Ausnahme von 9 und 10.

\subsubsection{General problem description}

In this example we consider a simple stationary FSI problem. \index{stationary PDE} \index{stationary PDE!FSI problem} The fluid
is given as an incompressible Newtonian fluid modeled by the Stokes equation. Here, we use the symmetric stress tensor which has a little consequence when using the do-nothing outflow condition, see also section \ref{PDE_Stat_Stokes}. \index{fluid} \index{fluid!incompressible} \index{fluid!Newtonian}
The computation domain is $\Omega = [-6,6]\times [0,2]$ and we choose for simplicity $f=0$.

>>>>

\subsubsection{General problem description}
\index{stationary PDE}\index{stationary PDE!FSI problem} \index{fluid} \index{fluid!incompressible} \index{fluid!Newtonian}
In this example we consider a simple stationary FSI problem. The fluid
is given as an incompressible Newtonian fluid modeled by the Stokes equation. Here, we use the symmetric stress tensor which has a little consequence when using the do-nothing outflow condition, see also section \ref{PDE_Stat_Stokes}.
The computation domain is $\Omega = [-6,6]\times [0,2]$ and we choose for simplicity $f=0$.
